Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-11-19 manuscript/manuscript.tex
[manuscript] update @franknoe `s affiliation, #171
adding citations for CK test discussion (this fixes #171)

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}]{Martin K. Scherer}
\author[1\authfn{1}]{Tim Hempel}
\author[1,2]{Brooke E. Husic}
\author[1]{Simon Olsson}
\author[1*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}
\affil[2]{Department of Chemistry, Stanford University, 333 Campus Drive, Stanford, California 94305, USA}

@@

Once we have used the ITS to choose the lag time, we can check whether a given transition probability matrix $\mathbf{P}(\tau)$ is approximately Markovian using the Chapman-Kolmogorov (CK) test~\cite{noe-folding-pathways}.
The CK property for a Markovian matrix is,
\begin{equation}
\mathbf{P}(k \tau) = \mathbf{P}^k(\tau),
\end{equation}
where the left-hand side of the equation corresponds to an MSM estimated at lag time $k\tau$, where $k$ is an integer larger than~$1$, whereas the right-hand side of the equation is our estimated MSM transition probability matrix to the $k^\textrm{th}$ power.
By assessing how well the approximated transition probability matrix adheres to the CK property, we can validate the appropriateness of the Markovian assumption for the model.

>>>>

\author[1\authfn{1}*]{Christoph Wehmeyer}
\author[1\authfn{1}]{Martin K. Scherer}
\author[1\authfn{1}]{Tim Hempel}
\author[1,2]{Brooke E. Husic}
\author[1]{Simon Olsson}
\author[1,3*]{Frank Noé}
\affil[1]{Department of Mathematics and Computer Science, Freie Universität Berlin, Arnimallee 6, 14195 Berlin, Germany}
\affil[2]{Department of Chemistry, Stanford University, 333 Campus Drive, Stanford, California 94305, USA}
\affil[3]{Department of Chemistry, Rice University, 6100 Main Street, Houston, Texas 77005, USA}

@@

Once we have used the ITS to choose the lag time, we can check whether a given transition probability matrix $\mathbf{P}(\tau)$ is approximately Markovian using the Chapman-Kolmogorov (CK) test~\cite{noe-folding-pathways}.
The CK property for a Markovian matrix is,
\begin{equation}
\mathbf{P}(k \tau) = \mathbf{P}^k(\tau),
\end{equation}
where the left-hand side of the equation corresponds to an MSM estimated at lag time $k\tau$, where $k$ is an integer larger than~$1$, whereas the right-hand side of the equation is our estimated MSM transition probability matrix to the $k^\textrm{th}$ power.
By assessing how well the approximated transition probability matrix adheres to the CK property, we can validate the appropriateness of the Markovian assumption for the model~\cite{msm-jhp,noe-folding-pathways}.
